TersectBrowser+ : A single browser for in-depth introgression analysis of re-sequenced genome datesets

### 2025-04-28 Article/Article.tex
Including Feature section intro.

\section{Features}

Tersect Browser+ is a web application based on Tersect Browser

\subsubsection{Gene Browser}

@@

\subsubsection{Gene Model}
\subsubsection{Search Features}
\subsubsection{Barcode Generator}

>>>>

\section{Features}
Tersect Browser+ is a web application that depends on resequenced data in VCF format and uses a reference genome in FASTA format. Utilizing a MEAN stack (MongoDB, Express, Angular, and Node) architecture, it creates a webpage displaying heatmaps and phylogenetic trees for introgressions within the loaded crop dataset. This provides an interface for users to identify differences across accessions within the same species dataset. It also includes a JBrowse interface for investigating specific variants, displaying selected genes directly alongside the generated heatmap. A search feature highlights high-impact variants on the webpage, helping to distinguish the selected reference genomes. Tersect Browser+ also offers barcode generation functionality for various cultivars and specific species in the dataset.

\begin{figure} [http]
  \centering
  \includegraphics[width=\textwidth]{path/to_image.png}
  \caption{Tersect Browser+ overview. The browser provides a single way to analyse variant data without leaving the page.[More description]}
  \label{fig:your_label}
\end{figure}

\subsubsection{Gene Brwoser}

@@

\subsubsection{Gene Model}

\subsubsection{Search Features}

\subsubsection{Barcode Generator}
